---
title: "MDEBdb Data Dictionary"
author:
  - Joshua Hatch
  - Nicole Mucci
date: '`r Sys.Date()`'
site: bookdown::bookdown_site
output:
  bookdown::bs4_book:
    template: "template.html"
    repo:
      base: https://github.com/jmhatch-NOAA/PEMAD-MDEB-Data_Dictionary
      branch: main
      subdir: bookdown
documentclass: krantz
monofont: "Source Code Pro"
monofontoptions: "Scale=0.7"
link-citations: yes
colorlinks: yes
graphics: yes
description: "Data dictionary for the MDEB spatial db."
github-repo: jmhatch-NOAA/PEMAD-MDEB-Data_Dictionary
rmd_files: ["index.Rmd"]
---

# Introduction

The Marine Development and Ecology Branch database (MDEBdb) contains geospatial data related to better understanding the interactions between marine development (like offshore wind) and NOAA Fisheries scientific surveys and trust resources. The creation of this database was funded, in part, by the Federal Permitting Improvement Steering Council (FPISC), and embodies the "shared database, shared schema" approach to data management.

This data dictionary is meant to catalog and communicate the structure and content of the MDEBdb, and provide meaningful descriptions of the data objects for users.

## NOAA Geoplatform

[Requirements for Public Content](https://docs.google.com/document/d/1MkWFyFY0Ptij6bPfC6T9kyAFupXiYEigF84klpqG76c/edit?tab=t.0#heading=h.q73ivxplnx2) 

[Publishing Data to the NOAA GeoPlatform](https://docs.google.com/document/d/1PLguB_zwiwheDyROco_fL-L5VHHmar5niE_yq86mN9M/edit?tab=t.0#heading=h.g7n4bqsp97bi)

```{r, echo = FALSE, results = 'hide'}
# generate token
token = arcgisutils::auth_client()

# delete files
old_rmd = list.files(pattern = '\\.Rmd')
old_rmd = old_rmd[old_rmd != 'index.Rmd']
file.remove(old_rmd)

# copy files
file.copy(from = here::here('bookdown', 'Rmd') |> list.files(full.names = TRUE), to = here::here('bookdown'), overwrite = TRUE)

# rename files
rmd = c('survey_mitigation.Rmd', 'ecomon.Rmd', 'csbll.Rmd','coastspan.Rmd','seal.Rmd', 'turtle.Rmd', 'clam_quahog.Rmd','scallop.Rmd', 'shrimp.Rmd', 'hook_line.Rmd','bottom_trawl.Rmd','mmst.Rmd',
'narw.Rmd','gombll.Rmd','edna.Rmd', 'pam.Rmd', 'smit_sop.Rmd', 'data_hub.Rmd', 'examples.Rmd')
rmd_files = paste0(stringr::str_pad(1:length(rmd), width = 2, side = 'left', pad = "0"), '-', rmd)
file.rename(from = rmd, to = rmd_files)
```

```{r, echo = FALSE, results = 'hide'}
chunks = paste0("```{r, echo = FALSE, child = '", rmd_files, "'}\n```\n")
cat(chunks, sep = '\n')
```
